---
title: "Political Violence in Germany"
---

Instructor: Dr. Michael C. Zeller    
Email: [m.zeller@lmu.de](mailto:m.zeller@lmu.de) (please use your LMU email address for communication)    
Webpage: <https://michaelzeller.de/>    
Office hour: Wednesdays, 11.00 - 12.00    
Office: GSI (Oettingenstr. 67) Room H105    


<!-- NOTES FROM PREVIOUS CLASS EVALUATION (2024) -->
<!-- - provide more content in the PowerPoints rather than just analysis of the Texts or discussion Points -->
<!-- - weniger abstrakt/theoretisch/statistisch die Inhalte vermitteln -->
<!-- - mehr Fokus auf die BRD (gehört zu politischem System der BRD, der Bezug ist aber kaum da -> dadurch schlechteres Verständnis und doppelter Lernaufwand) -->
<!-- - In preparation for the final exam, short tests could be organised at each session so that students can assess their own knowledge. -->
<!-- - More recommended readings based on the individual groups would be helpful - have found the search for literature on my organisation challenging. -->
<!-- - Layout der PowerPoint könnte besser sein. Wichtige Punkte fallen nicht sehr auf. Zum wiederholen nicht geeignet. -->
<!-- - this is not necessarily something that needs to be improved, as I wouldn’t call it a problem, but I did find a little misleading the name of the course: the course is called Political Violence in Germany, but we barely spoke about Germany. Maybe calling it Political Violence would be better -->

<!-- NOTES FROM far right course EVALUATION (2025) FOR ONLINE MATERIALS: -->
<!-- - Maybe encourage to make mistakes regarding the english language (I sometimes did not raise my hand because I was "too shy" to speak up compared to the students with very good english, as they had a bigger academic vocabulary than I did -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timeDate)
library(tibble)
library(dplyr)
library(knitr)

# https://www.benlinzmeier.rocks/post/an-rmarkdown-syllabus-template/
# http://svmiller.com/blog/2016/07/r-markdown-syllabus/

library(lubridate) # for submission date of assignments

# library(RefManageR)
# bib <- ReadBib("library.bib")
# myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

# https://www.lmu.de/en/workspace-for-students/abc-study-guide/lecture-periods/index.html
# https://www.ferienwiki.de/feiertage/de/bayern

#This code chunk sets up a table of meeting days for the course.
#You can set days of the week for course meetings (e.g. Monday and Wednesday).
#Semester start and end dates are selected and then university holidays like spring break are specified.
#Days of the week that the course meets. Must be full day name in quotes.
Days <- c("Thursday")
#Semester start date for classes as YYYY/M/D.
SemesterStart <- as.Date("2025/10/16")
#Semester end date for classes as YYYY/M/D.
SemesterEnd <- as.Date("2026/2/7")
#Fall break start and stop date.
WinterBreak <-
  seq.Date(
    from = as.Date("2025/12/22"),
    to = as.Date("2026/1/6"),
    by = "day"
  )
#Spring break start and stop date.
# SpringBreak <-
#   seq.Date(
#     from = as.Date("2022/02/28"),
#     to = as.Date("2022/03/06"),
#     by = "day"
#   )
#Creates a list of days within the semester.
SemesterDays <-
  seq.Date(from = SemesterStart, to = SemesterEnd, by = "day")
#Add day before Thanksgiving.
#Add day before Thanksgiving.
# DayBeforeThnks<-as.Date(holiday(
#     year = getRmetricsOptions("currentYear"),
#     Holiday = c("USThanksgivingDay")))-1
#Full list of holidays that there are no classes including breaks.
Holidays <-
  c(as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USLaborDay", "USMLKingsBirthday")
  )), WinterBreak)
#Create a list of semester days excluding holidays.
SemesterDays <- SemesterDays[!SemesterDays %in% Holidays]
#Make dataframe with all semester days.
ClassDays <- data.frame(index = 1:length(SemesterDays))
#Insert dates.
ClassDays$Date <- SemesterDays
#Insert weekday designation.
ClassDays$Weekday <- weekdays(ClassDays$Date)
#Limit to the class meeting days.
MeetingDays <- ClassDays[ClassDays$Weekday %in% Days, ]
#Create numeric list of weeks.
Week <- cut.Date(MeetingDays$Date, breaks = "week")
levels(Week) <- 1:length(levels(Week))
MeetingDays$Week <- Week
MeetingDays$Class <- 1:nrow(MeetingDays)

Lecture_Topic <- c("Introduction and types of political violence", # Class 1
                   "Causes: setting the stage for political violence", # Class 2
                   "Radicalisation", # Class 3
                   "Selecting violent/nonviolent strategies", # Class 4
                   "Radical subcultures and mobilisation", # Class 5
                   "Leadership", # Class 6
                   "Foreign fighters", # Class 7 - Mass shooters, foreign fighters, and terrorism in authoritarian states
                   "Election-related violence", # Class 8
                   "Escalation and restraint", # Class 9
                   "Local support and public reaction", # Class 10
                   "State responses: policies", # Class 11
                   "State responses: repression", # Class 12
                   "Addressing violence online", # Class 13
                   "Disengagement, deradicalisation (individual), demobilisation (organisational)", # Class 14
                   "NO CLASS MEETING TODAY") # Class 15"

          
links <- c("#class1","#class2","#class3","#class4","#class5","#class6","#class7","#class8","#class9","#class10","#class11","#class12","#class13","#class14","#class15")

MeetingDays <- bind_cols(MeetingDays, Lecture = Lecture_Topic)
#### Grade table ####
Grades <- tribble( ~ Grade,
                   ~ Range,
                   "A",
                   "90-100",
                   "B",
                   "80-89",
                   "C",
                   "70-79",
                   "D",
                   "60-69",
                   "F",
                   "< 60")
####Assignment weight table####
Weights <- tribble(
                    ~ Item,
                    ~ Weight,
                    "Writing scaffolding",
                    "20 %",
                    "Semester Project",
                    "25 %",
                    "Labratory Assignments",
                    "20 %",
                    "Midterm Exam",
                    "15 %",
                    "Final Exam",
                    "20 %"
                  )
```

## Course particulars

- Course level: **BA**
- Course format: **seminar**
<!-- - Course number: **15030** -->
<!-- - Credits: **2.0 SWS** -->
- Module assignment: **Einführung in das Politische System Deutschlands**

## Course description
<!-- Kompetenzen -->

This course will introduce students to the major aspects of (non-state) political violence by presenting research covering violent extremism and terrorism, radicalisation and deradicalisation, repression, demobilisation. We will consider why people and groups use political violence and how, its range of effects, how states and others react. Students will acquire both substantive knowledge of these research fields---especially through the repeated examination of important cases, such as political violence in Germany and in other countries---and the ability to evaluate research therein. Students should be prepared for reading and discussion of difficult topics, which can be unsettling.

## Course schedule overview

```{r Schedule, echo=FALSE, message=FALSE, warning=FALSE}

library(kableExtra)

# MeetingDays$Lecture <- paste0("[", MeetingDays$Lecture, "](", links, ")")

kable(MeetingDays[,c("Date","Class","Week","Lecture")],
      # caption = "Course Schedule.",
      align = c("l","c","c","l"),
      format = "simple"
      ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```


## Course and Teacher evaluation

Student input for the purpose of course improvement is taken very seriously and will potentially be done periodically. Please take the time to evaluate this course and the instructor, especially at the end of the semester. Evaluations will in no way affect your grade.


